I\textsuperscript{2}CNER Project Report \\ Dynamic Transition Analysis With TIMES

### 2019-04-25 doc/2018-09-report/2019-04-i2cner-report.tex
updated reports
Former-commit-id: c59bae1eb3e129670245586fe9aa8d179648867e
Former-commit-id: fded899746f4578d27cd950d810e347eebac6e56

\item \textbf{Incorporation of the contribution-to-peak \cite{gargiulo_documentation_2005} factor:} This parameter is defined as the fraction of a resource's capacity that is guaranteed to be available during peak demand. This introduces a notion of an energy resource's reliability, thereby reducing excessive deployment of wind and solar due to their unreliability. The values in the model \cite{kato_energy_2016} may not be entirely accurate, since they are annually averaged.\\

\item \textbf{Basic Carbon Capture and Sequestration (CCS) Implementation} : Some CCS data \cite{kato_energy_2016}  was incorporated into \href{https://github.com/arfc/i2cner/tree/master/JPN-Main-Model/active/i2cner-nonuc}{one of the models}. However, no CCS gets deployed in our models. We believe  it should be deployed for an intermediate time-period, since in the absence of nuclear, only CCS can provide reliable, clean energy. We have identified a few shortcomings in the CCS implementation, some of which contribute to this problem:

@@

\item \textbf{Remove pure oil from all models:} We do not think Japan will ever increase its dependence on oil due to its cost, emissions intensity and due to the Japanese goal of increasing energy independence. Current trends support this assumption. While a few models already exclude oil-based energy, other models should also exclude pure oil-based electricity generation for the sake of consistency.

@@

\item \textbf{Revise CCS structure:} Simplified CCS needs to be implemented that emits only 5-10\% of the CO$_2$ that the corresponding fossil fuel technology emits. In the model, this should look like any other fossil fuel electricity generation process, except it should be more expensive and have reduced emissions. Such an implementation should \textbf{not} include retrofitting of CCS (i.e. adding carbon capture to previously deployed fossil fuel capacity - discussed below). While we do not have Japan-specific data for CCS, we can simplify our model by using data from the US and do one of the following:
\begin{itemize}

>>>>

\item \textbf{Incorporation of the contribution-to-peak \cite{gargiulo_documentation_2005} factor:} This parameter is defined as the fraction of a resource's capacity that is guaranteed to be available during peak demand. This introduces a notion of an energy resource's reliability, thereby reducing excessive deployment of wind and solar due to their unreliability. The values in the model \cite{kato_energy_2016} do not take into account the true daily or seasonal variation of wind and solar, as they are annually averaged.\\

\item \textbf{Basic Carbon Capture and Sequestration (CCS) Implementation} : Some CCS data \cite{kato_energy_2016}  was incorporated into \href{https://github.com/arfc/i2cner/tree/master/JPN-Main-Model/active/i2cner-nonuc}{one of the models}. However, no CCS gets deployed in our models. We believe  it should be deployed for an intermediate time-period, since in the absence of nuclear, only CCS can provide reliable, clean energy in conjunction with renewables. We have identified a few shortcomings in our model, some of which contribute to this problem:

@@

\item \textbf{Remove pure oil based electricity generation from all models:} We do not think Japan will ever increase its dependence on oil due to its cost, emissions intensity and due to the Japanese goal of increasing energy independence. Current trends support this assumption. While a few models already exclude oil-based energy, other models should also replace it with combined-cycle electricity generation for the sake of consistency.

@@

\item \textbf{Revise CCS structure:} Simplified CCS needs to be implemented that emits only 5-10\% of the CO$_2$ that the corresponding fossil fuel technology emits \cite{kato_energy_2016}. In the model, this should look like any other fossil fuel electricity generation process, except it should be more expensive and have reduced emissions. Such an implementation should \textbf{not} include retrofitting of CCS (i.e. adding carbon capture to previously deployed fossil fuel capacity - discussed below). While we do not have Japan-specific data for CCS, we can simplify our model by using data from the US and do one of the following:
\begin{itemize}
